0/1 Knapsack

### 2015-03-13 Programming Project C/01knapsack.tex
minor update?

A dynamic solution to 0/1 knapsack can be implemented in a variety of languages using the pseudocode provided in Algorithm 3.
\newline
\textbf{Dynamic Knapsack Pre-Condition}: $Weights$ and $Prices$ both have $n$ number of elements
\newline
\textbf{Dynamic Knapsack Post-Condition}: The returned value will be the correct solution for the largest value of price combinations such that the aggregate of the corresponding weights does not exceed knapsack capacity $c$.
\begin{algorithm}
\caption {\textsc{Dynamic-Knapsack}(n, Weights, Prices, c)}
\label{algo:dynamic}
\begin{algorithmic}[1]
\Procedure{Dynamic-Knapsack}{n, Weights, Prices, c}
\If{$n == 1$ and $Weights[1] <= c$}
	\State{\Return{$Prices[1]$}}
\EndIf
\If{$n <= 0$}
	\State{\Return{$0$}}
\EndIf
\State{$tab[n][c] = new Nested Array$}
\For{$x = 1$ upto $n$}
	\For{$y = 1$ upto $c$}
		\State{$tab[x][y] = 0$}
	\EndFor
\EndFor
\For{$i = 1$ upto $n$}
	\For{$j = 0$ upto $c$}
		\If{$Weights[i] <= j$ and $Prices[i] + tab[i][j - Weights[i]] > tab[i][j]$}
			\State{$tab[i+1][j] = Price[i] + tab[i][j - weights[i]]$}
		\EndIf
		\If{$!$$(Weights[i] <= j)$ and $!$$(Prices[i] + tab[i][j - Weights[i]] > tab[i][j])$}
			\State{$tab[i+1][j] = tab[i][j]$}
		\EndIf
	\EndFor
\EndFor
\State{\Return{$tab[n][c]$}}
\EndProcedure
\end{algorithmic}
\end{algorithm}
\newline
%% TODO: Write pseudocode invariants here for Dynamic solution
\newline
\newline

>>>>

A dynamic solution to 0/1 knapsack can be implemented in a variety of languages using the pseudocode provided in Algorithm 3.
\newline
\textbf{Dynamic Knapsack Pre-Condition}: $Weights$ and $Prices$ both have $n$ number of elements
\newline
\textbf{Dynamic Knapsack Post-Condition}: The returned value will be the correct solution for the largest value of price combinations such that the aggregate of the corresponding weights does not exceed knapsack capacity $c$.
\begin{algorithm}
\caption {\textsc{Dynamic-Knapsack}(n, Weights, Prices, c)}
\label{algo:dynamic}
\begin{algorithmic}[1]
\Procedure{Dynamic-Knapsack}{n, Weights, Prices, c}
\If{$n == 1$ and $Weights[1] <= c$}
	\State{\Return{$Prices[1]$}}
\EndIf
\If{$n <= 0$}
	\State{\Return{$0$}}
\EndIf
\State{$tab[n][c] = new Nested Array$}
\For{$x = 1$ upto $n$}
	\For{$y = 1$ upto $c$}
		\State{$tab[x][y] = 0$}
	\EndFor
\EndFor
\For{$i = 1$ upto $n$}
	\For{$j = 0$ upto $c$}
		\If{$Weights[i] <= j$ and $Prices[i] + tab[i][j - Weights[i]] > tab[i][j]$}
			\State{$tab[i+1][j] = Price[i] + tab[i][j - weights[i]]$}
		\EndIf
		\If{$!$$(Weights[i] <= j)$ and $!$$(Prices[i] + tab[i][j - Weights[i]] > tab[i][j])$}
			\State{$tab[i+1][j] = tab[i][j]$}
		\EndIf
	\EndFor
\EndFor
\State{\Return{$tab[n][c]$}}
\EndProcedure
\end{algorithmic}
\end{algorithm}
\newline
\textbf{Dynamic Solution First Outer-Loop Invariant}: tab[1 .. x-1] has the same number of non-null elements in it as both Weights[1 ... x - 1] and Prices[1 ... x-1].
\newline
\textbf{Dynamic Solution First Outer-Loop Invariant Initialization}: Before the first iteration of the loop the invariant holds true vacuously because tab[0 ... x-1], weights[0 ... x-1] and prices[0 ... x-1] all do not exist.
\newline
\textbf{Dynamic Solution First Outer-Loop Invariant Maintenance}: At the beginning of each iteration because x is incremented by one at the same rate that one element is added to tab.
\newline
\textbf{Dynamic Solution First Outer-Loop Invariant Termination}: At the termination of the loop the invariant holds true because x has been incremented at the same rate that an element has been added to tab.
\newline
\newline
\textbf{Dynamic Solution First Inner-Loop Invariant}: tab[x] has y number of non-null elements in it.
\newline
\textbf{Dynamic Solution First Inner-Loop Invariant Initialization}: Before the first iteration of the loop the invariant holds true because y = 0 and tab[x] has 0 elements in it.
\newline
\textbf{Dynamic Solution First Inner-Loop Invariant Maintenance}: At the beginning of each iteration of the loop the invariant holds true because because y is incremented at the same rate that elements are added to tab[x].
\newline
\textbf{Dynamic Solution First Inner-Loop Invariant Termination}: After the termination of the loop the invariant holds true because elements have been added to tab[x] at the same rate in which y has been incremented.
\newline
\newline
